Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-02-07 paper/main.tex
Edit generalization of data-driven models section

\subsection*{Performance of models trained on one experiment versus many experiments}
Figure~\ref{fig:eq_goodbad_1} illustrates the predictive performance of two
models on data within their training sets, while
Figures~\ref{fig:eq_goodbad_2},~\ref{fig:eq_goodbad_3},
and~\ref{fig:eq_goodbad_4} illustrate the performance of those same two models
on data outside their training sets. The differences between these two models
result from the fact that one of them, $EQ_4$ from Table~\ref{table:eqmodels}
(drawn in blue), was trained on 58 separate experiments simultaneously, whereas
the other one, shown below (drawn in red), is one of many models trained only on
the single experiment shown in Figure~\ref{fig:eq_goodbad_1}:
\begin{align}
 Force = \frac{C_1 + C_2\psi^2 - C_3\psi}{C_4 + \ddot{\theta} + C_5\dot{\theta} + \cos(C_6 -
  \frac{C_7}{\psi^2} - C_8\psi)} - C_9.
\label{eq:badeq}
\end{align}
Thus, $EQ_4$ shows strong qualitative and quantitative agreement with all of the
experiments in Figure~\ref{fig:eq_goodbad}, indicating that this model is not
over-fit but in fact generalizes well to new data. Equation~\eqref{eq:badeq}, on
the other hand, fails to accurately predict the recorded data outside its
training set.  Insufficient data and over-fitting are potential pitfalls of
data-driven modeling, but are overcome in this case with a diverse sampling of
training data.

Since Equation~\eqref{eq:badeq} is unable to accurately predict forces outside
its training set, it is unlikely to offer any insight into the underlying
physical processes.  $EQ_4$, however, must capture some of the underlying
structure of the physics in order to generalize to data upon which it was not
trained.  In data-driven modeling, training on many experiments simultaneously
helps to reject candidate equations that may fit some, but not all, of the data,
and helps to retain those models that reflect the underlying physics and offer
insight into the structure of the additive components that compose the observed
behavior of a complex dynamical system.

>>>>

\subsection*{Generalization of Data-Driven Models}
To evaluate the generalization properties of our data-driven models, we compare
one of our models, $EQ_4$, which was trained on 58 training experiments, to a
model that was trained on only a single experiment:
\begin{align}
 Force = \frac{C_1 + C_2\psi^2 - C_3\psi}{C_4 + \ddot{\theta} + C_5\dot{\theta} + \cos(C_6 -
  \frac{C_7}{\psi^2} - C_8\psi)} - C_9.
\label{eq:badeq}
\end{align}
Figure~\ref{fig:eq_goodbad_1} illustrates the predictive performance of these
two models on data within their training sets, and indeed this figure
illustrates the \emph{only} data used to train equation~\eqref{eq:badeq}.
Figures~\ref{fig:eq_goodbad_2},~\ref{fig:eq_goodbad_3},
and~\ref{fig:eq_goodbad_4} illustrate the performance of these same two models
on test data outside their training sets.

$EQ_4$ shows strong qualitative and quantitative agreement with all of the
experiments in Figure~\ref{fig:eq_goodbad}, indicating that this model is not
over-fit but in fact generalizes well to new data. On the other hand,
equation~\eqref{eq:badeq} fails to accurately predict the data outside its
training set.  Insufficient data and over-fitting are potential pitfalls of
data-driven modeling, but are overcome in this case with a diverse sampling of
training data that span the parameter space of interest for the modeling task.

Since Equation~\eqref{eq:badeq} is unable to accurately predict forces outside
its training set, it is unlikely to offer any insight into the underlying
physical processes.  $EQ_4$, however, must capture some of the underlying
structure of the physics in order to generalize to data outside its training
set. In data-driven modeling, training on many experiments simultaneously
helps to reject candidate equations that may fit some, but not all, of the data,
and helps to retain those models that reflect the underlying physics and offer
insight into the structure of the components that make up the observed
behavior of a complex dynamical system.
